Network Configuration Synthesis with Abstract Topologies

### 2016-11-13 paper/abstraction/paper.tex
typo fix
add examples for hyperx and bcube
add text to match images

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/example3}
  \vspace{-2em}
  \caption{An abstraction for the datacenters in Figure~\ref{fig:example}.}
  \label{fig:example3}
  \vspace{-1em}
\end{figure}

@@

\begin{figure}[t!]
%  \begin{code}
%    \Template{S}
%      Match[100] \PREFIX=\$GP, \PEER=\{AG, AL\}
%        \PEER \Arrow *
%      Match[100] \PREFIX=\$LP, \PEER=\{AG, AL\}
%        \PEER \Arrow \{AG, AL\}
%      Match[110] \PREFIX=true \PEER=\{P1\},
%        \PEER \Arrow *, \COMM \Arrow (1,0)
%      Match[100] \PREFIX=true \PEER=\{P2\},
%        \PEER \Arrow *, \COMM \Arrow (0,1)
%      ...
%  \end{code}%

%  \vspace{-2em}
%  \begin{code}
%    \Router{S1, S2}
%      Match[100] \PREFIX=GP1, \PEER=\{AG1, AL1, ...\}
%        \PEER \Arrow *
%      Match[100] \PREFIX=GP2, \PEER=\{AG1, AL1, ...\}
%        \PEER \Arrow *
%      ...
%      Match[100] \PREFIX=LP1, \PEER=\{AG1, AL1, ...\}
%        \PEER \Arrow \{AG1, AL1, ...\}
%      Match[100] \PREFIX=LP2, \PEER=\{AG1, AL1, ...\}
%        \PEER \Arrow \{AG1, AL1, ...\}
%      ...
%      Match[110] \PREFIX=true, \PEER=\{P1\},
%        \PEER \Arrow *, \COMM \Arrow (1,0)
%      Match[100] \PREFIX=true, \PEER=\{P2\},
%        \PEER \Arrow *, \COMM \Arrow (0,1)
%      ...
%    \end{code}

  \begin{center}
  \includegraphics[width=\columnwidth]{figures/configs}
  \end{center}
  \vspace{-1em}
  \caption{Spine template and concrete configurations (left), and evolution-friendly templates (right).}
  \label{fig:bgp-configs}
\end{figure}

@@

@@

\begin{thm}
  For any context $\Gamma$, topologies $G$ and $G^A$, homomorphism $f : G \rightarrow G^A$, and policy $pol$,
  $$\Con(\text{compile}(pol,G^A), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f),G)$$
  \label{thm:concretization}
\end{thm}
%
\vspace{-1em}
Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix.

@@

@@

%\begin{figure}[t!]
%  \begin{center}
%      \begin{tabular}{| l l | c | c | c |}
%      \hline
%      \textbf{Topology} & \textbf{Variant} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
%      Fattree
%         & Google &  & \cmark & \cmark  \\
%         & Facebook &  & \cmark & \cmark \\
%         & F10 &  & \cmark & \cmark \\ \hline
%      Recursive
%         & BCube & $k$ & \cmark & \xmark \\
%         & DCell & $k$ & \cmark & \xmark \\ \hline
%         %& HCN & $h$ & \cmark & \xmark \\
%      Hypercube
%         & Standard & $N$ & \cmark & \cmark \\
%         & HyperX & $L$ & \cmark & \cmark \\ \hline
%      Random \footnote{foo}
%         & Scafida &  & ??? & ??? \\
%         & JellyFish &  & ??? & ??? \\
%      \hline
%      \end{tabular}
%  \end{center}
%  \caption{Abstract Analysis Precision.}
%  \label{fig:analysis-precision}
%\end{figure}

@@

We also model several recursive topologies. These include the BCube~\cite{bcube} and Dcell~\cite{dcell} topologies. Each topology includes a recursion depth parameter ($k$), which we must fix. For a recursive topology with depth $d$, we model it as an abstract topology consisting of an abstract node for each of the depth $d-1$ subcomponents. This allows for safe expansion within a subcomponent, but not from increasing the recursion depth. The analysis is able to accurately determine reachability (i.e., at least 1 disjoint path) for each recursive topology, but is overly conservative in determining k-disjoint paths. For the BCube topology, it is able to to determine the correct number of disjoint paths between some pairs of nodes, but not all.

@@

Hypercube variants can be used as an alternative to Clos-style topologies for networks with high-radix (port density) routers. The HyperX~\cite{hyperx} topology can be viewed as a generalization of the hypercube and butterfly topologies, which includes parameters $L$ for the lattice dimension of the network, and $S_i$ for the node multiplicity of each dimension $i$.
%$K_i$ for the bandwidth of links for each dimension,
%and $T$ for the number of terminal nodes (servers) connected to each router.
For a fixed number of dimensions $L$, we abstract each full mesh of $S_L$ nodes into its own abstract node. The $S_{x-1}$ groups of abstract nodes can be captured using pods of the abstract $S_x$ nodes. For all hypercube variants, the fault-tolerance analysis is precise.

>>>>

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/example3}
  \vspace{-2em}
  \caption{An abstraction for the network in Figure~\ref{fig:example}.}
  \label{fig:example3}
  \vspace{-1em}
\end{figure}

@@

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=\columnwidth]{figures/configs}
  \end{center}
  \vspace{-1em}
  \caption{Spine template and concrete configurations (left), and evolution-friendly templates (right).}
  \label{fig:bgp-configs}
\end{figure}

@@

\begin{thm}
  For any context $\Gamma$, topologies $G$ and $G^A$, homomorphism $f : G \rightarrow G^A$, and policy $pol$,

  \vspace{1em}
  \noindent
  $\Con(\text{compile}(pol,G^A), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f),G)$
  \label{thm:concretization}
\end{thm}
%
\vspace{-.8em}
Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix.

@@

\begin{figure}[t!]
  \begin{minipage}[t]{\linewidth}
    \hdr{HyperX}{}
    \vspace{.6em}
    \includegraphics[width=\linewidth]{figures/hyperx}
  \end{minipage}%

  \vspace{1.4em}
  \begin{minipage}[t]{\linewidth}
    \hdr{BCube}{}
    \vspace{.3em}
    \includegraphics[width=\linewidth]{figures/bcube}
  \end{minipage}%

  \caption{Example abstractions for HyperX and BCube.}
  \vspace*{-1em}%
  \label{fig:example-abstractions}
\end{figure}

@@

@@

We also model several recursive topologies. These include the BCube~\cite{bcube} and Dcell~\cite{dcell} topologies. Each topology includes a recursion depth parameter ($k$), which we fix. For a recursive topology with depth $k$, we model it as an abstract topology consisting of a pod to represent all depth $k-1$ subcomponents. This allows for safe expansion within a subcomponent, but not from increasing the recursion depth.
For BCube, we model each tier of the datacenter as a separate role. Figure~\ref{fig:example-abstractions} shows an example of a BCube abstraction for $k=1$.
The analysis is able to accurately determine reachability (i.e., at least 1 disjoint path) for each recursive topology, but is overly conservative in determining k-disjoint paths. For the BCube topology, it is able to to determine the correct number of disjoint paths between some pairs of nodes, but not all.

@@

Hypercube variants can be used as an alternative to Clos-style topologies for networks with port density routers. The HyperX~\cite{hyperx} topology is a generalization of the hypercube and butterfly topologies, which includes parameters $L$ for the lattice dimension of the network, and $S_i$ for the node multiplicity of each dimension $i$.
%$K_i$ for the bandwidth of links for each dimension,
%and $T$ for the number of terminal nodes (servers) connected to each router.
For a fixed number of dimensions $L$, we abstract each full mesh of $S_L$ nodes into its own abstract node. Nodes in dimension $S_{x-1}$ are abstracted using pods of abstract nodes from dimension $S_x$. Figure~\ref{fig:example-abstractions} shows an example for $L=2$.
For all hypercube variants, the fault-tolerance analysis is precise.
